\documentclass[11pt,a4paper]{moderncv}

\usepackage{fontspec}
\usepackage[brazil]{babel}
\usepackage[scale=0.8, top=1cm, bottom=2cm]{geometry}

\moderncvstyle{classic}
\moderncvcolor{red}

\firstname{Cauê}
\familyname{Baasch de Souza}

\address{Florianópolis, Brasil}
\mobile{+55 (48) 99634-5456}
\email{cauebs@pm.me}

\title{Curriculum Vitae}

\begin{document}
\makecvtitle{}
\pagestyle{empty}

\section{Education}

\cventry
    {2015--2016}
    {B.Sc. in Mechanical Engineering (Incomplete)}
    {}{}{}
    {Federal University of Santa Catarina}

\cventry
    {2016--}
    {B.Sc. in Computer Science}
    {}{}{}
    {Federal University of Santa Catarina}

\section{Skills}
    \subsection{Programming}
        \cvitem{Advanced}{Python, Rust}
        \cvitem{Intermediate}{C, C++, Haskell, Elm, MicroPython}
        \cvitem{Basic}{TypeScript, Arduino}

    \subsection{Tools}
        \cvitem{Advanced}{Poetry, Cargo}
        \cvitem{Intermediate}{Git, Docker, Podman, Conda, Pytest}
        \cvitem{Basic}{Ninja, Meson, GNU Make, Puppet, Ansible}

    \subsection{Development environments}
        \cvitem{Advanced}{Visual Studio Code}
        \cvitem{Intermediate}{PyCharm, Jupyter}
        \cvitem{Basic}{Vim}

    \subsection{Other}
        \cvitem{}{Relational databases (SQLite, PostgreSQL).}
        \cvitem{}{Linux (Arch Linux, Fedora, Silverblue, Ubuntu).}

    \subsection{Knowledge and interests}
        \cvitem{}{Programming language design and implementation.}
        \cvitem{}{Static analysis.}
        \cvitem{}{Algorithm development and analysis.}
        \cvitem{}{Benchmarking and optimization.}
        \cvitem{}{Development of tools and process automation.}
        \cvitem{}{Geographic information systems (GIS).}
        \cvitem{}{Embedded systems.}
        \cvitem{}{Teaching programming (e.g. Python, Rust, MicroPython.)}

    \subsection{Languages}
        \cvitem{English}{Fluent for reading, writing and speaking.}
        \cvitem{Portuguese}{Fluent for reading, writing and speaking.}
        \cvitem{French}{Basic level.}

\newpage


\section{Professional experience}
    \cventry{2016--2017}{Intern}
    {Laboratório de Transportes e Logística (LabTrans) - UFSC}
    {(Transportation and Logistics Laboratory)}{}{
        \begin{itemize}
            \item Python.
            \item Qt, Cassandra.
            \item Pandas, Geopandas, Shapely, Matplotlib, Folium, PostGIS.
        \end{itemize}
    }

    \cventry{2018}{Freelancer}
    {Engie}
    {}{}{Development of a web scraper of power plant listings.}

    \cventry{2020}{Intern}
    {Expertise Solutions}
    {}{}{Assisted in adding native support for Windows to the EFL application toolkit (C/C++).}

    \subsection{Teaching}
        \cvitem{2017--2019}{Python course @ UFSC (volunteer) (80 credit hours)}
        \cvitem{2018}{Rust workshop @ UFSC (volunteer) (4 credit hours)}
        \cvitem{}{Rust workshop @ SECCOM - UFSC (4 credit hours)}

    \cventry{2020}{Intern}
    {Expertise Solutions}
    {}{}{Assisted in adding native support for Windows to the EFL application toolkit (C/C++).}

    \subsection{Teaching}
        \cvitem{2017--2019}{Python course @ UFSC (volunteer) (80 credit hours)}
        \cvitem{2018}{Rust workshop @ UFSC (volunteer) (4 credit hours)}
        \cvitem{}{Rust workshop @ SECCOM - UFSC (4 credit hours)}

    \subsection{Other extracurricular work}
        \cventry{2017--}{Founding member}
        {Caravela HackerClub}
        {(student collective and hackerspace)}{}{}

        \cventry{2018--2019}{Treasurer}
        {Centro Acadêmico Livre da Computação (CALICO)}
        {(students' union)}{}{}

        \cventry{2019--2022}{Vice-president}
        {Centro Acadêmico Livre da Computação (CALICO)}
        {(students' union)}{}{}

        \cventry{2019--2022}{Board director}
        {Diretório Central dos Estudantes (DCE) - Luís Travassos}
        {(students' union)}{}{}


\section{Academic Experience}
    \cventry{2019}{Departamento de Informática e Estatística - UFSC}{Research Intern}
    {}{}{
        \begin{itemize}
            \item Data fusion in IoT.
            \item Microservices for communication protocol integration in IoT.
            \item Arduino, Zigbee, MicroPython, sockets.
        \end{itemize}
    }


\section{Events}
    \subsection{Organizing}
        \cvitem{2018}{32º Python Floripa @ UFSC}
        \cvitem{}{33º Python Floripa @ UFSC}
        \cvitem{}{1º Rust Floripa @ CIASC}
        \cvitem{}{2º Rust Floripa @ CIASC}
        \cvitem{}{Todos a Bordo \#1 (Caravela Hackerclub)}
        \cvitem{}{Todos a Bordo \#2 (Caravela Hackerclub)}
        \cvitem{}{37º Python Floripa @ UFSC}
        \cvitem{2019}{Computer Science Academic Week at UFSC (SECCOM)}

    \subsection{Speaking}
        \cvitem{2017}{CPython data structures (in portuguese) @ 25º Python Floripa (SENAI)}
        \cvitem{2018}{Creating and packaging CLI applications in Rust (in portuguese) @ Native Floripa}
        \cvitem{2019}{MicroPython: the pythonista Arduino (in portuguese) @ 36º Python Floripa (Celta)}
        \cvitem{}{Language programming (programming language design) (in portuguese) @ Todos a Bordo \#4 (Caravela Hackerclub)}
        \cvitem{}{With a license I have my rights (intelectual property and free software) (in portuguese) @ Todos a Bordo \#5 (Caravela Hackerclub)}

\section{Personal repositories}
\cvitem{}{\url{https://github.com/cauebs}}

\thispagestyle{plain}

\end{document}
